Improving disaggregation models of malaria incidence by ensembling non-linear models of prevalence

### 2019-10-23 tim-lucas-model-ensembles.tex
Get elsevier template working.

\documentclass[11pt]{article}
\fontfamily{times}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{subcaption}

\usepackage{natbib}
%\usepackage[numbers, sort&compress]{natbib}
%\setcitestyle{authoryear}

\geometry{verbose,tmargin=30mm,bmargin=25mm,lmargin=25mm,rmargin=25mm}
%\input{figures.tex}
\pagestyle{empty}
\begin{document}
%\templatefigures{}

\small{

\begin{center}
%The title should be centred and in bold letters. It should be informative but not too long (preferably no more than two lines).
\textbf{Improving disaggregation models of malaria incidence by ensembling non-linear models of prevalence}
\end{center}

@@

%\begin{center}
{
\noindent Tim C. D. Lucas*\textsuperscript{1}; 
Anita K. Nandi\textsuperscript{1},
Emma L. Collins\textsuperscript{1},
Suzanne H. Keddie\textsuperscript{1},
Katherine A. Twohig\textsuperscript{1},
Elisabeth G. Chestnutt\textsuperscript{1},
Rosalind E. Howes\textsuperscript{1},
Michele Nguyen\textsuperscript{1},
Susan F. Rumisha\textsuperscript{1},
Andre Python\textsuperscript{1},
Rohan Arambepola\textsuperscript{1},
Amelia Bertozzi-Villa\textsuperscript{1, 2},
Penelope Hancock\textsuperscript{1},
Punam Amratia\textsuperscript{1},
Katherine E. Battle\textsuperscript{1},
Ewan Cameron\textsuperscript{1},
Peter W. Gething\textsuperscript{1, 3, 4},
Daniel J. Weiss\textsuperscript{1}}\vspace{0.4cm}\\

{
\noindent 1. Malaria Atlas Project, Big Data Institute, University of Oxford, Oxford, UK \\
2. Institute for Disease Modeling, Bellevue, WA, USA\\
3. Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia\\
4. Curtin University, Perth, Australia\\
* timcdlucas@gmail.com}\\

%\end{center}
\section{Abstract}

@@

{\bf Keywords}: Spatial statistics; Ensemble; Stacking; Epidemiology.
}\\

@@

\section*{Acknowledgments}
The authors acknowledge the National Malaria Control Programme of Madagascar for sharing their routine case data for this analysis.

\bibliography{Malaria} 
%\bibliographystyle{unsrt}
\bibliographystyle{apalike}

>>>>

\documentclass[review]{elsarticle}

\usepackage{graphicx}
\usepackage{amsmath}

\usepackage{subcaption}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\bibliographystyle{elsarticle-num}
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

\usepackage{natbib}
%\usepackage[numbers, sort&compress]{natbib}
%\setcitestyle{author[oxford]year}

%\geometry{verbose,tmargin=30mm,bmargin=25mm,lmargin=25mm,rmargin=25mm}
%\input{figures.tex}
%\pagestyle{empty}
\begin{document}
%\templatefigures{}

@@

% Spatial and Spatio-temporal Epidemiology
% Special issue: Disease Surveillance and Infectious disease Modeling

\begin{frontmatter}

\title{Improving disaggregation models of malaria incidence by ensembling non-linear models of prevalence}

\author[oxford]{Tim C. D. Lucas\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{timcdlucas@gmail.com}
\author[oxford]{Anita K. Nandi}
\author[oxford]{Emma L. Collins}
\author[oxford]{Suzanne H. Keddie}
\author[oxford]{Katherine A. Twohig}
\author[oxford]{Elisabeth G. Chestnutt}
\author[oxford]{Rosalind E. Howes}
\author[oxford]{Michele Nguyen}
\author[oxford]{Susan F. Rumisha}
\author[oxford]{Andre Python}
\author[oxford]{Rohan Arambepola}
\author[oxford,idm]{Amelia Bertozzi-Villa}
\author[oxford]{Penelope Hancock}
\author[oxford]{Punam Amratia}
\author[oxford]{Katherine E. Battle}
\author[oxford]{Ewan Cameron}
\author[oxford,telethon,curtin]{Peter W. Gething}
\author[oxford]{Daniel J. Weiss}

\address[oxford]{Malaria Atlas Project, Big Data Institute, University of Oxford, Oxford, UK}
\address[idm]{Institute for Disease Modeling, Bellevue, WA, USA}
\address[telethon]{Telethon Kids Institute, Perth Children’s Hospital, Perth, Australia}
\address[curtin]{Curtin University, Perth, Australia}

\begin{abstract}

@@

\end{abstract}

\begin{keyword}
Spatial statistics; Disaggregation regression; Stacking; Surveillance data
\end{keyword}

\end{frontmatter}

\linenumbers

@@

\section*{Acknowledgments}
The author[oxford]s acknowledge the National Malaria Control Programme of Madagascar for sharing their routine case data for this analysis.

\bibliography{Malaria} 
%\bibliographystyle{unsrt}
%\bibliographystyle{apalike}
